G\"{o}del's God on the Computer\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2013-11-04 Abstract/IWIL-2013/abstract.tex
Abstract for IWIL

Attempts to prove the existence (or non-existence) of God by means of
abstract ontological arguments are an old tradition in philosophy and
theology.  G\"{o}del's proof \cite{Goedel1970,GoedelNotes} is a modern culmination of
this tradition, following particularly the footsteps of Leibniz.
%
G\"{o}del defines God as a being who possesses all \emph{positive} properties.
He does not extensively discuss what positive properties are, 
but instead he states a few reasonable (but debatable) axioms that they should satisfy.
Various slightly different versions of axioms and definitions have
been considered by G\"{o}del and by several philosophers who commented
on his proof; cf. \cite{sobel2004logic,AndersonGettings,Fitting,Adams,ContemporaryBibliography}.
We have analyzed Scott's version of G\"{o}del's proof \cite{ScottNotes} for the first-time
with an unprecedent degree of detail 
and formality with the help of theorem provers; cf.~\url{https://github.com/FormalTheology/GoedelGod}.

@@

\bibitem{THF}
G.~Sutcliffe.
\newblock The TPTP TPI Scripting Language (check!).
\newblock {\em Proc. of IWIL-10}, 2013.

>>>>

Attempts to prove the existence (or non-existence) of God by means of
abstract ontological arguments are an old tradition in philosophy and
theology.  G\"{o}del's proof \cite{Goedel1970,GoedelNotes} is a modern culmination of
this tradition, following particularly the footsteps of Leibniz.
%
G\"{o}del defines God as a being who possesses all \emph{positive} properties.
He does not extensively discuss what positive properties are, 
but instead he states a few reasonable (but debatable) axioms that they should satisfy.
Various slightly different versions of axioms and definitions have
been considered by G\"{o}del and by several philosophers who commented
on his proof; cf. \cite{sobel2004logic,AndersonGettings,Fitting,Adams,ContemporaryBibliography}.
We have analyzed Scott's version of G\"{o}del's proof \cite{ScottNotes} for the first-time
with an unprecedented degree of detail 
and formality with the help of theorem provers; cf.~\url{https://github.com/FormalTheology/GoedelGod}.

@@

\bibitem{TPI}
G.~Sutcliffe.
\newblock The TPTP TPI Scripting Language (check!).
\newblock {\em Proc. of IWIL-10}, 2013.
